Supplement to Automatic Matching of Bullet Lands

### 2015-12-31 imaging-paper.Rnw
cleaning up the last pieces of content

% put your definitions there:
\startlocaldefs
\usepackage{enumitem}
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}

\renewcommand{\topfraction}{0.99}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.99}	% max fraction of floats at bottom
% parameters for text pages
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

@@

% "Title of the paper"
\title{Automatic Matching of Bullet Lands}\thanksref{T1}
\thankstext{T1}{Resources for this manuscript, including R code to reproduce any of the models, tables and figures, can be found at  \url{https://github.com/erichare/imaging-paper}.}
\runtitle{Automatic Matching of Bullet Lands}
\runauthor{E. Hare et al.}

@@

\linenumbers
\tableofcontents
\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "app/images/Hamby252_3DX3P1of2/"

@@

\item add: more discussion on additional bullet images. NIST database claims to have 70 bullets -- that would be two sets of the study, but only 35 bullets are currently available. Should we contact Alan Zheng to see whether we can get access to more bullet files?
\item add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$). Something for the appendix? What would be fun, would be to show all of the aligned signatures for all ten barrels.

@@

\item add: we might need a proper definition of the joint striation marks (the result of striation-identify)
\item change: we could make the table into a labelled dotplot of importance to save space. We don't need the mean and standard deviations anymore -- the density plots and the ROCs take care of that.

@@

\item definitions: 
A bullet's {\it signature} is defined as the residual surface measurements after removing the big structure using the loess fit. The {\it cross section} defines the location along the $x$ axis  at which the signature is taken.

@@

\hh{In an approach to analyze the striation pattern we extract a {\emph bullet profile} \cite{ma:2004} by taking a cross section across the surface measurements for a fixed value of $x$.}
%An initial naive approach to analyzing the striation patterns leads us to fixing a particular value of a coordinate, and then producing a plot of the surface measurements across. 
Figure \ref{fig:fixedX} shows a plot of the side profile of a bullet land. It can be seen that the global structure of the land dominates the appearance of the plot. The grooves can be clearly identified on the left and right side, and the curvature of the surface is the most visible feature in the middle.

@@

The smooth curve on the plot represents a segment of a perfect circle with the same radius as the bullet. \hh{While the circle is an obvious first choice for fitting the structure, it does not completely capture the bullet surface after it was fired. A discussion of a circular fit and the remaining residual structure can be found in supplement~\ref{supp:cylindrical}.} 
%It is clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.

@@

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
This defines the {\it signature} of bullet~1-5. Blue areas show  95\% bootstrap confidence intervals (based on $B=1,000$ bootstrap samples).
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  ylab("Residuals of loess fit") + xlab("y") + theme_bw()
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1).}
\end{figure}
%

@@

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item {\bf Smooth the two signatures} by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to {\bf find the best alignment} of the two signatures: shift one of the signatures by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, {\bf identify peaks and valleys} for each of the signatures. We then define an interval around the location of the extrema on each side as one third of the distance to the location of the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item {\bf Match striations across signatures:} based on the intervals around the extrema as defined above, we identify joint intervals between two signatures as those areas, in which two or more of the individual intervals overlap: a joint interval is defined as the smallest interval that encompasses all of the overlapping intervals. A joint interval is then called a match(ing stria) between the signatures, if all of the intervals are of the same type of extrema, i.e.\ they are either all peaks or all valleys. In Figure~\ref{fig:match} all matches are shown as color-filled rectangles corresponding to their type of extrema (peaks are shown in orange, and valleys in green). Non-matching intervals are left grey.
\item {\bf Extract features from the aligned signatures and the matches between them:} there is a slew of different features one could extract. Here, we describe a few of the ones that can be found in the literature and some that we found to be of practical relevance:
\begin{enumerate}[label=(\roman*)]
\item maximal number of CMS (consecutive matching striae), and, similarly, the number of consecutively non-matching striae (CNMS), 
\item number of matches and non-matches,
\item average difference between signatures $D$, defined as the Euclidean vertical distance of surface measurements between aligned signatures. Let $f(t)$ and $g(t)$ be smoothed, aligned signatures:
\[
D^2 = \frac{1}{\text{\#}t}\sum_t \left(f(t) - g(t)\right)^2,
\]
\item the sum $S$ of matched extrema: for each of the matched stria, determine the average of the absolute height of the peak or valley. $S$ is then defined as the sum of all these averages. 
\end{enumerate}
\end{enumerate}
%
The difference $D$ between signatures is here defined as the Euclidean distance (in $\mu m$). In the paper by \citet{ma:2004}, distance is defined as a measure relative to the first signature, which serves as a comparison reference and is therefore a unitless quantity.

@@

However, error rates based on bullet-to-bullet matches do not carry a lot of weight because of the small size of the study: fifteen unknown bullets are successfully matched to two pairs of ten bullets. Matching bullets can only be tested realistically in a much bigger test case. 
Another thing to note about the  the random forest's error rates is that they are based on probability cutoffs of 0.5, i.e.\ whenever the predicted probability of a match exceeds 0.5, a match is declared. Basing this decision on 0.5 is not necessary. In practice, examiners are allowed a third option of `inconclusive'. On a probability spectrum of outcomes we could therefore introduce an interval of `inconclusive' results in the middle of the spectrum -- which turns out to be not necessary in the Hamby study, because, here, the results from the random forest are very clear cut. Figure~\ref{fig:tree-forest} shows a comparison of the predicted probabilities of a match by the tree ($x$-axis) and the random forest ($y$-axis). %\hh{The tree predicts 132 known matches correctly, with 40 false negatives and one false positive match. The random forest predicts all 172 known matches correctly as well as all 10,212 known non-matches.} 
%Overall, there is a lot of agreement; out of 10,800 land-to-land comparisons, only four cases result in a different decision.

@@

Besides a probabilistic quantification of matches, we get from a random forest an assessment of the importance of each of the features derived from the bullets' 3d topological surface measurements. Figure~\ref{fig:importance} shows an overview of the importance of each variable measured as the mean decrease in the gini index when the variable in question is included in a tree.
\begin{figure}
<<echo=FALSE, fig.width=7, fig.height=1.5, out.width='.7\\textwidth'>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp$Variable[c(7,8)] <- c("#matches", "#non-matches")
imp1 <- subset(imp, !(Variable %in% c("x1", "sd.D")))
imp2 <- subset(imp, Variable %in% c("x1", "sd.D"))
qplot(MeanDecreaseGini,1, data=imp, geom="point") + 
  geom_text(aes(y=1.1, label=Variable), angle=45, hjust=0, data=imp1) + 
  geom_text(aes(y=0.9, label=Variable), angle=-45, hjust=0, data=imp2) + 
  ylim(c(0, 2.75)) + theme_bw() + ylab("") +
  theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank()) +
  xlab("Importance (mean decrease in Gini index)")
@
\caption{\label{fig:importance}Importance of features in the random forest. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree.}
\end{figure}
%' \begin{table}[tbhp]
%' \caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
%' \centering
%' <<importance, echo=FALSE, results='asis', warning=FALSE>>=
%' imp <- data.frame(importance(rtrees))
%' imp$Variable <- row.names(imp)
%' imp <- imp[order(-imp$MeanDecreaseGini),]
%' names(imp)[1] <- "Importance"
%' imp <- imp[,2:1]
%' imp$meanMatch <- sapply(imp$Variable, function(var) {
%'   mean(subset(bstats, match)[,var])
%' })
%' imp$sdMatch <- sapply(imp$Variable, function(var) {
%'   sd(subset(bstats, match)[,var])
%' })
%' imp$meanNonMatch <- sapply(imp$Variable, function(var) {
%'   mean(subset(bstats, !match)[,var])
%' })
%' imp$sdNonMatch <- sapply(imp$Variable, function(var) {
%'   sd(subset(bstats, !match)[,var])
%' })
%' imp$meanMatch <- round(imp$meanMatch,1)
%' imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
%' imp$meanNonMatch <- round(imp$meanNonMatch,1)
%' imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
%' row.names(imp) <- 1:nrow(imp)
%' imp$Variable[c(2,4)] <- c("#matches", "#non-matches")
%' names(imp)[-(1:2)] <- c("KM", "(sd)", "KNM", "(sd)")
%' print(xtable(imp, align="clrrd{3.2}rd{3.2}", digits=c(0,0,1,1,2,1,2)), 
%'       floating = FALSE)
%' @
%' \end{table}

@@

We have presented an algorithm which detects the most prominent but least relevant structure of a bullet from a ballistics identification perspective, removes these features, and produces residuals which allows for the easy identification of markings. We have generalized this algorithm to align the residuals from two bullets to automatically determine whether they are matches. We created a random forest model using many of the features to provide a probabilistic assessment of the quality of a match, along with the most relevant features. Finally, we have provided an easy-to-use open-source backend, and web frontend to many of these features.

>>>>

% put your definitions there:
\startlocaldefs
\usepackage{enumitem}
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\usepackage{lineno}
\modulolinenumbers[5]

\usepackage{xr}
\externaldocument{imaging-supplement}

\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}

\renewcommand{\topfraction}{0.99}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.99}	% max fraction of floats at bottom
% parameters for text pages
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.98}	% require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.98}	% require fuller float pages

@@

% "Title of the paper"
\title{Automatic Matching of Bullet Lands}\thanksref{T1}
\thankstext{T1}{Resources for this manuscript, including R code to reproduce all of the models, tables and figures, can be found at  \url{https://github.com/erichare/imaging-paper}.}
\runtitle{Automatic Matching of Bullet Lands}
\runauthor{E. Hare et al.}

@@

\linenumbers
%\tableofcontents
%\newpage
<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "app/images/Hamby252_3DX3P1of2/"

@@

%\item add: more discussion on additional bullet images. NIST database claims to have 70 bullets -- that would be two sets of the study, but only 35 bullets are currently available. Should we contact Alan Zheng to see whether we can get access to more bullet files? Not enough space for this one.
%\item add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$). Something for the appendix? What would be fun, would be to show all of the aligned signatures for all ten barrels. (moved to supplement)

@@

%\item add: we might need a proper definition of the joint striation marks (the result of striation-identify)
%\item change: we could make the table into a labelled dotplot of importance to save space. We don't need the mean and standard deviations anymore -- the density plots and the ROCs take care of that.

@@

%\item definitions: 
%A bullet's {\it signature} is defined as the residual surface measurements after removing the big structure using the loess fit. The {\it cross section} defines the location along the $x$ axis  at which the signature is taken.

@@

\hh{In an approach to analyze the striation pattern we extract a \emph{bullet profile} \citep{ma:2004} by taking a cross section across the surface measurements for a fixed value of $x$.}
%An initial naive approach to analyzing the striation patterns leads us to fixing a particular value of a coordinate, and then producing a plot of the surface measurements across. 
Figure \ref{fig:fixedX} shows a plot of the side profile of a bullet land. It can be seen that the global structure of the land dominates the appearance of the plot. The grooves can be clearly identified on the left and right side, and the curvature of the surface is the most visible feature in the middle.

@@

The smooth curve on the plot represents a segment of a perfect circle with the same radius as the bullet. \hh{While the circle is an obvious first choice for fitting the structure, it does not completely capture the bullet surface after it was fired. A discussion of a circular fit and the remaining residual structure can be found in supplement~\ref{supp:circular}.} 
%It is clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.

@@

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  ylab("Residuals of loess fit") + xlab("y") + theme_bw()
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1). The residuals define the {\it signature} of bullet~1-5. Blue areas around the residuals show  95\% bootstrap confidence intervals (based on $B=1,000$ bootstrap samples).
}
\end{figure}
%

@@

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item {\bf Smooth the two signatures} by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to {\bf find the best alignment} of the two signatures: shift one of the signatures by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, {\bf identify peaks and valleys} for each of the signatures. We then define an interval around the location of the extrema on each side as one third of the distance to the location of the next extrema (see Figure~\ref{fig:smoothcutb}). Peaks and valleys constitute the \emph{striation marks} of the bullet.
\item {\bf Match striations across signatures:} based on the intervals around the extrema as defined above, we identify joint intervals between two signatures as those areas, in which two or more of the individual intervals overlap: a joint interval is defined as the smallest interval that encompasses all of the overlapping intervals. A joint interval is then called a match(ing stria) between the signatures, if all of the intervals are of the same type of extrema, i.e.\ they are either all peaks or all valleys. In Figure~\ref{fig:match} all matches are shown as color-filled rectangles corresponding to their type of extrema (peaks are shown in orange, and valleys in green). Non-matching intervals are left grey.
\item {\bf Extract features from the aligned signatures and the matches between them:} there is a slew of different features one could extract. Here, we describe a few of the ones that can be found in the literature and some that we found to be of practical relevance:
\begin{enumerate}[label=(\roman*)]
\item maximal number of CMS (consecutive matching striae), and, similarly, the number of consecutively non-matching striae (CNMS), 
\item number of matches and non-matches,
\item average difference between signatures $D$, defined as the Euclidean vertical distance of surface measurements between aligned signatures. Let $f(t)$ and $g(t)$ be smoothed, aligned signatures:
\[
D^2 = \frac{1}{\text{\#}t}\sum_t \left(f(t) - g(t)\right)^2,
\]
\item the sum $S$ of matched extrema: for each of the matched stria, determine the average of the absolute height of the peak or valley. $S$ is then defined as the sum of all these averages. 
\end{enumerate}
\end{enumerate}
%
The difference $D$ between signatures is here defined as the Euclidean distance (in $\mu m$). In the paper by \citet{ma:2004}, distance is defined as a measure relative to the first signature, which serves as a comparison reference and is therefore a unitless quantity.

@@

However, error rates based on bullet-to-bullet matches do not carry a lot of weight because of the small size of the study: fifteen unknown bullets are successfully matched to two pairs of ten bullets. Matching bullets can only be tested realistically in a much bigger test case. 
Another thing to note about the  the random forest's error rates is that they are based on probability cutoffs of 0.5, i.e.\ whenever the predicted probability of a match exceeds 0.5, a match is declared. Basing this decision on 0.5 is not necessary. In practice, examiners are allowed a third option of `inconclusive'. On a probability spectrum of outcomes we could therefore introduce an interval of `inconclusive' results in the middle of the spectrum -- which turns out to be not necessary in the Hamby study, because, here, the results from the random forest are very clear cut. Figure~\ref{fig:tree-forest} shows a comparison of the predicted probabilities of a match by the tree and the random forest. %\hh{The tree predicts 132 known matches correctly, with 40 false negatives and one false positive match. The random forest predicts all 172 known matches correctly as well as all 10,212 known non-matches.} 
%Overall, there is a lot of agreement; out of 10,800 land-to-land comparisons, only four cases result in a different decision.

@@

Besides a probabilistic quantification of matches, we get from a random forest an assessment of the importance of each of the features derived from the bullets' 3d topological surface measurements. Figure~\ref{fig:importance} shows an overview of the importance of each variable measured as the mean decrease in the gini index when the variable in question is included in a tree.
\begin{figure}
<<echo=FALSE, fig.width=7, fig.height=2, out.width='.7\\textwidth'>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp$Variable[c(7,8)] <- c("#matches", "#non-matches")
imp1 <- subset(imp, !(Variable %in% c("x1", "sd.D")))
imp2 <- subset(imp, Variable %in% c("x1", "sd.D"))
qplot(MeanDecreaseGini,1, data=imp, geom="point") + 
  geom_text(aes(y=1.2, label=Variable), angle=45, hjust=0, data=imp1) + 
  geom_text(aes(y=0.8, label=Variable), angle=-45, hjust=0, data=imp2) + 
  ylim(c(0, 2.75)) + theme_bw() + ylab("") +
  theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank()) +
  xlab("Importance (mean decrease in Gini index)")
@
\caption{\label{fig:importance}Importance of features in the random forest. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree.}
\end{figure}
%' \begin{table}[tbhp]
%' \caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
%' \centering
%' <<importance, echo=FALSE, results='asis', warning=FALSE>>=
%' imp <- data.frame(importance(rtrees))
%' imp$Variable <- row.names(imp)
%' imp <- imp[order(-imp$MeanDecreaseGini),]
%' names(imp)[1] <- "Importance"
%' imp <- imp[,2:1]
%' imp$meanMatch <- sapply(imp$Variable, function(var) {
%'   mean(subset(bstats, match)[,var])
%' })
%' imp$sdMatch <- sapply(imp$Variable, function(var) {
%'   sd(subset(bstats, match)[,var])
%' })
%' imp$meanNonMatch <- sapply(imp$Variable, function(var) {
%'   mean(subset(bstats, !match)[,var])
%' })
%' imp$sdNonMatch <- sapply(imp$Variable, function(var) {
%'   sd(subset(bstats, !match)[,var])
%' })
%' imp$meanMatch <- round(imp$meanMatch,1)
%' imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
%' imp$meanNonMatch <- round(imp$meanNonMatch,1)
%' imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
%' row.names(imp) <- 1:nrow(imp)
%' imp$Variable[c(2,4)] <- c("#matches", "#non-matches")
%' names(imp)[-(1:2)] <- c("KM", "(sd)", "KNM", "(sd)")
%' print(xtable(imp, align="clrrd{3.2}rd{3.2}", digits=c(0,0,1,1,2,1,2)), 
%'       floating = FALSE)
%' @
%' \end{table}

@@

We have presented an algorithm which detects the most prominent but least relevant structure of a bullet from a ballistics identification perspective, removes these features, and produces residuals which allows for the easy identification of markings. We have generalized this algorithm to align the residuals from two bullets to automatically determine whether they are matches. We created a random forest model using many of the features to provide a probabilistic assessment of the quality of a match, along with the most relevant features. %Finally, we have provided an easy-to-use open-source backend, and web frontend to many of these features.

### 2015-12-31 imaging-supplement.Rnw
cleaning up the last pieces of content

% put your definitions there:
\startlocaldefs
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]

@@

\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}

>>>>

% put your definitions there:
\startlocaldefs
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\usepackage{lineno}
\modulolinenumbers[5]

@@

\newpage
\section{One-on-one comparison of Hamby study}\label{supp:extended}
\hh{
add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$).  What would be fun, would be to show all of the aligned signatures for all ten barrels. (moved to supplement)
}
\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}
